Continuous voting by approval and participation

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
melhorada discussao
adicionada autoria do Poppi

\author{Renato Fabbri\affil{1}{IFSC/USP, Participa.br, labMacambira.sf.net}
%James Smith\affil{2}{University of Oregon}
%\and
%Jane Smith\affil{1}{}
}

@@

\section{Discussion}
The above estimates are the best fit the researchers could deliver,
suitable for current needs and not found (yet) in literature.
The following questions should be answered in near future:
\begin{itemize}
	\item Are there more adequate metrics for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted in time?
    \item Are there really no previous formalized model of this setting? If there is, what comparisons can we make on design, metrics and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
	\item What is the impact of this technological approach in public health care, social participation and the scientific community?
\end{itemize}

@@

\begin{acknowledgments}
	Author is grateful to CNPq (process
	140860/2013-4, project 870336/1997-5), UNDP
	(contract 2013/00056, project BRA/12/018), SNAS/SGPR,
	and the Postgraduate Committee of the IFSC/USP.
\end{acknowledgments}

>>>>

\author{Renato Fabbri\affil{2}{University of S\~ao Paulo}
\and
Ricardo Poppi\affil{1}{Brazilian General Secretariat of the Republic}
}
%James Smith\affil{2}{University of Oregon}
%\and
%Jane Smith\affil{1}{}
%}

@@

\section{Discussion}
The above estimates are the best fit the researchers could deliver,
suitable for current needs and not found (yet) in literature.
The following questions should be addressed in near future:
\begin{itemize}
	\item Are there more adequate metrics for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted in time?
    \item Are there really no previous formalized model of this setting? If there is, what comparisons can we make on design, metrics and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
	\item What is the impact of this technological approach in public health care, social participation and the scientific community?
    \item To which extent society benefits from this continuous voting process? Is it worth the time spent by voters? How to evaluate this relation in terms of spent and gained resources?
\end{itemize}

@@

\begin{acknowledgments}
	Author is grateful to CNPq (process
	140860/2013-4, project 870336/1997-5), UNDP
	(contract 2013/00056, project BRA/12/018), SNAS/SGPR,
	and the Postgraduate Committee of the IFSC/USP.
	Thanks to the Brazilian social participation community for the conception and practice of this specific voting setting.
\end{acknowledgments}
